Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-08-03 writing/DraftExposurePaper/DraftExposurePaper.Rmd
miami dade code

miami_rain <- countyweather_rain(counties = "12086", county_weather = dade_weather,
                                 start_year = 1988, end_year = 2011,
                                 rain_limit = 0, dist_limit = 1000)
miami_plot <- ggplot(miami_rain, aes(x = cw_precip, y = tot_precip)) +
        geom_hline(aes(yintercept = 75), color = "lightgray") +
        geom_vline(aes(xintercept = 75), color = "lightgray") +
        geom_abline(aes(intercept = 0, slope = 1), color = "gray", alpha = 0.5) +
        # geom_point(aes(size = prcp_reporting), alpha = 0.2) +
        geom_point(alpha = 0.5) +
        # geom_text(aes(x = monitor_rain + 100, label = storm_id)) +
        xlim(c(0, 275)) + ylim(c(0, 275)) +
        theme_few() +
        scale_size_continuous(guide = "none") +
        xlab("Rainfall (mm) based on \naveraged county monitors") +
        ylab("Rainfall (mm) based on \nNLDAS-2 county data") +
        ggtitle("Monitor versus NLDAS rainfall estimates \nfor Miami-Dade County, FL, by storm")

>>>>

miami_rain <- countyweather_rain(counties = "12086", county_weather = dade_weather,
                                 start_year = 1988, end_year = 2011,
                                 rain_limit = 0, dist_limit = 2000)
miami_plot <- ggplot(miami_rain, aes(x = cw_precip, y = tot_precip)) +
        geom_hline(aes(yintercept = 75), color = "lightgray") +
        geom_vline(aes(xintercept = 75), color = "lightgray") +
        geom_abline(aes(intercept = 0, slope = 1), color = "gray", alpha = 0.5) +
        # geom_point(aes(size = prcp_reporting), alpha = 0.2) +
        geom_point(alpha = 0.5) +
        # geom_text(aes(x = monitor_rain + 100, label = storm_id)) +
        xlim(c(0, 275)) + ylim(c(0, 275)) +
        theme_few() +
        scale_size_continuous(guide = "none") +
        xlab("Rainfall (mm) based on \naveraged county monitors") +
        ylab("Rainfall (mm) based on \nNLDAS-2 county data") +
        ggtitle("Monitor versus NLDAS rainfall estimates \nfor Miami-Dade County, FL, by storm")
